\texttt{thornado}-transport: IMEX schemes for two-moment neutrino transport respecting Fermi-Dirac statistics

### 2018-10-18 Documents/M1/Astronum_2018/sections/Conclusion.tex
Backup the modification in time integration section.

We have developed IMEX schemes for two-moment neutrino transport in \texttt{thornado} that respect Fermi-Dirac statistics.
The schemes employ algebraic closure based on Fermi-Dirac statistics, a first-order discontinuous Galerkin method, the simple Lax-Friedrichs flux, and convex-invariant time integration to maintain point-wise realizability of the moments.
Since the realizability-preserving property is obtained from the convexity of the realizable domain, it's possible to construct a scheme with a high-order DG method.
See \cite{chu_etal_2018} for some examples with third-order DG methods.

>>>>

We have developed IMEX schemes for two-moment neutrino transport in \texttt{thornado} that respect Fermi-Dirac statistics.
The schemes employ algebraic closure based on Fermi-Dirac statistics, a third-order discontinuous Galerkin method, the Lax-Friedrichs flux, and convex-invariant time integration to maintain cell-average realizability of the moments.
Since the realizability-preserving property is obtained from the convexity of the realizable domain, it's possible to construct a scheme with a high-order DG method.
See \cite{chu_etal_2018} for some examples with third-order DG methods.

### 2018-10-18 Documents/M1/Astronum_2018/sections/Numerical.tex
Backup the modification in time integration section.

In this section we present the numerical results obtained with the PD-ARS schemes given in Section~\ref{se:TimeIntegration}.
The tests in Section \ref{se: Accuracy Tests} are designed to compare the accuracy of the schemes in streaming, absorption, and scattering-dominated regimes in one spatial dimension.
The test in Section \ref{se: Neutrino Stationary State Test} demonstrates the convex-invariance of PD-ARS schemes schemes.
All the tests in this subsection were constructed with third-order accurate spatial discretization (polynomials of degree $k=2$) and time step $\dt = 0.1 \times \dx $.

@@

\subsubsection{Sine Wave Streaming}
The sine wave streaming test is designed for the steaming dominated regime, with $\sigma_{\Ab} = \sigma_{\Scatt} = 0$.
A periodic domain with length=1 is used and the initial condition is $\cJ = \bcH =$ a spatial sine wave function.
We evolve the test until the sine wave has completed 10 crossings of the domain.
Figure~\ref{fig: SineWaveStreaming} plots the absolute error for the number density versus the number of elements $N$.
We see the errors obtained with SSPRK3 and PD-ARS with SSPRK3 as the explicit part decrease as $N^{-3}$, as expected.
All the other schemes have errors decreasing as $N^{-2}$.
Among the second-order schemes, SSP2332 has the smallest error.

In the streaming limit, PD-ARS scheme limit to its explicit part, SSPRK2 and SSPRK3, respectively.
That's why the absolute errors of PD-ARS and SSPRK are indistinguishable on the plot.

@@

\subsubsection{Sine Wave Damping}
This test, adapted from \cite{skinnerOstriker_2013}, is designed for absorption-dominated regimes, with $\sigma_{\Scatt} = 0$ and $f_0 = 0$, which results in exponential damping of the wave amplitude.
A periodic domain with length=1 and an initial condition with $\cJ = \bcH =$ a spacial sine wave function is used.
The amplitude of the analytical solution decreases as $e^{-\sigma_{\Ab} t}$.
For $\sigma_{\Ab}$ = 0.1, 1 and 10 we evolve the test until the initial condition has been damped by a factor $e^{-10}$. 
Figure~\ref{fig:SineWaveDamping} shows convergence results of the sine wave damping test in the relative error.
SSP2332, a second-order scheme, displays second-order convergence.
PD-ARS schemes converge with a first-order convergence rate given the price paid for convex-invariance.
\begin{figure}[h]
  \centering
    \includegraphics[width=0.9\textwidth]{figures/SineWaveDamping}
   \caption{Relative error versus number of elements, $N$, for the damping sine wave test. Results for different values of the absorption opacity $\sigma_{\Ab}$, employing various IMEX time stepping schemes, are compared.  Errors for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively.  The IMEX schemes employed are SSP2332 ($+$), PD-ARS with SSPRK2 (circles) and PD-ARS with SSPRK3 (hexagram).  Black dashed reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
  \label{fig:SineWaveDamping}
\end{figure}

\subsubsection{Sine Wave Diffusion}
The last test with known smooth solution,adopted from \cite{radice_etal_2013}, is the sine wave diffusion test with $\sigma_{\Ab} = 0, f_0 = 0$.
A periodic domain with $D=\{x:x\in[-3,3]\}$ and an initial condition with $\cJ_{0}$ = a spatial sine wave function and $\cH =-\f{1}{3\sigma_{\Scatt}}\pderiv{\cJ}{x}$ is used.
The analytic solution is given by $\cJ = \cJ_{0} \times e^{-\f{\pi^2 t}{27\sigma_{\Scatt}}}$ and $\cH = (3\,\sigma_{\Scatt})^{-1}\pd{\cJ}{x}$.
We evolve with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$, and adjust the end time so that $t_{\mbox{\tiny end}}/\sigma_{\Scatt}=1$. 
Then the amplitude of the sine wave has been reduced by a factor $e^{-\pi^{2}/27}\approx0.694$ for all values of $\sigma_{\Scatt}$. 
Figure~\ref{fig:SineWaveDiffusionJ} shows the convergence.
SSP2332 and PD-ARS schemes display third-order accuracy for the number density, $\cJ$, and second-order accuracy for $\cH_{x}$, and their errors are difficult to distinguish.
PD-ARS with SSP2332 behaves as good as SSP2332 in the diffusion region but requires 1/3 less implicit solvers.
\begin{figure}[h]
  \centering
  \centerline{\includegraphics[width=1.2\textwidth]{figures/SineWaveDiffusion}}
%  \begin{tabular}{cc}
%    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionJ}
%    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionH}
%  \end{tabular}
   \caption{Absolute error for the number density $\cJ$ (left) and the number flux $\cH_{x}$ (right) versus number of elements for the sine wave diffusion test.  Results with different values of the scattering opacity $\sigma_{\Scatt}$, employing different IMEX schemes, are compared.  Errors with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively.  The IMEX schemes employed are:  SSP2332 ($+$), PD-ARS with SSPRK2 (circles), and PD-ARS with SSPRK3 (hexagram). Black dashed lines on the left plot reference lines proportional to $N^{-2}$ (top) and $N^{-3}$ (bottom), respectively. Black dashed line on the right plot reference lines proportional to $N^{-2}$ .}
   \label{fig:SineWaveDiffusionJ}
\end{figure}

\subsection{Neutrino Stationary State Test} \label{se: Neutrino Stationary State Test}
Next we consider a more ``realistic'' test: two-dimensional neutrino transport with emission, absorption, and elastic scattering in a stationary ``realistic'' background.
This is designed to test the realizability-preserving properties of the PD-ARS schemes.
Figure~\ref{fig:NeutrinoStationaryTestEOS} plots the thermal state and the opacities we used.
This test is constructed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ with a grid of 128 elements in each direction.
We take 10 energy groups from 0~MeV to 300~MeV and initialize the neutrino number density $\cJ$ and flux density $\bcH$ both at zero(arbitrarily small).
For the realizability-preserving test, CB closure with PD-ARS schemes, SSP2332, a scheme proposed by Cavaglieri \& Bewley \cite{cavaglieriBewley2015}, and a scheme proposed by McClarren et al \cite{mcclarren_etal_2008} are all applied.
Only PD-ARS schemes produce realizability-preserving results and evolve the model to a stable state.
The realizability-preserving plot and the evolve process of PD-ARS schemes are given in Figure~\ref{fig:NeutrinoStationaryTestEvolve}.

>>>>

In this section we present the numerical results obtained with the PD-ARS schemes given in Section~\ref{se:TimeIntegration}.
The tests in Section \ref{se: Accuracy Tests} are designed to compare the accuracy of the schemes in streaming, absorption, and scattering-dominated regimes in one spatial dimension.
The test in Section \ref{se: Neutrino Stationary State Test} demonstrates the convex-invariance of PD-ARS schemes schemes.
All the tests in this subsection were constructed with third-order accurate spatial discretization (polynomials of degree $k=2$) and time step $\dt = 0.1 \times \dx $, using the DG scheme we present in \cite{chu_etal_2018}.

@@

\subsubsection{Sine Wave Streaming}
The sine wave streaming test is designed for the steaming dominated regime, i.e. $\sigma_{\Ab} = \sigma_{\Scatt} = 0$.
A periodic domain of unit length is used and the initial condition is $\cJ_{0} = \bcH_{0} = 0.5+0.49\times\sin\big(2\pi\,x\big)$.
We evolve the test until the sine wave has completed 10 crossings of the domain.
Figure~\ref{fig: SineWaveStreaming} plots the absolute error for the number density versus the number of elements $N$.
We see the errors obtained with SSPRK3 and PD-ARS with SSPRK3 as the explicit part decrease as $N^{-3}$, as expected.
All the other schemes have errors decreasing as $N^{-2}$.
Among the second-order schemes, SSP2332 has the smallest error.

In the streaming limit, the PD-ARS schemes limit to their explicit part, SSPRK2 and SSPRK3, respectively.
Therefore, the absolute errors of PD-ARS and SSPRK are indistinguishable on the plot.

@@

\subsubsection{Sine Wave Damping}
This test, adapted from \cite{skinnerOstriker_2013}, is designed for absorption-dominated regimes, with $\sigma_{\Scatt} = 0$ and $f_0 = 0$, which results in exponential damping of the wave amplitude.
A periodic domain of unit length and an initial condition with $\cJ_{0} = \bcH_{0} = 0.5+0.49\times\sin\big(2\pi\,x\big)$ is used.
The amplitude of the analytical solution decreases as $e^{-\sigma_{\Ab} t}$.
For $\sigma_{\Ab}$ = 0.1, 1 and 10 we evolve the test until the initial condition has been damped by a factor $e^{-10}$. 
Figure~\ref{fig:SineWaveDamping} shows convergence results of the sine wave damping test in the relative error.
SSP2332, a second-order scheme, displays second-order convergence.
PD-ARS schemes converge with a first-order convergence rate: the price paid for the convex-invariant property.
\begin{figure}[h]
  \centering
    \includegraphics[width=0.9\textwidth]{figures/SineWaveDamping}
   \caption{Relative error versus number of elements, $N$, for the damping sine wave test. Results for different values of the absorption opacity $\sigma_{\Ab}$, employing various IMEX time stepping schemes, are compared.  Errors for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively.  The IMEX schemes employed are SSP2332 ($+$), PD-ARS with SSPRK2 (circles) and PD-ARS with SSPRK3 (hexagram).  Black dashed reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
  \label{fig:SineWaveDamping}
\end{figure}

\subsubsection{Sine Wave Diffusion}
The last test with known smooth solution, adopted from \cite{radice_etal_2013}, is the sine wave diffusion test, i.e. $\sigma_{\Ab} = 0$ and $f_0 = 0$.
A periodic domain with $D=\{x:x\in[-3,3]\}$ and an initial condition with $\cJ_{0} = 0.5+0.49\times\sin\big(\f{\pi\,x}{3}\big)$ and $\cH_{0} =-\f{1}{3\sigma_{\Scatt}}\pderiv{\cJ_{0}}{x}$ is used.
The analytic solution is given by $\cJ = \cJ_{0} \times e^{-\f{\pi^2 t}{27\sigma_{\Scatt}}}$ and $\cH = (3\,\sigma_{\Scatt})^{-1}\pd{\cJ}{x}$.
We evolve with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$, and adjust the end time so that $t_{\mbox{\tiny end}}/\sigma_{\Scatt}=1$. 
Then the amplitude of the sine wave has been reduced by a factor $e^{-\pi^{2}/27}\approx0.694$ for all values of $\sigma_{\Scatt}$. 
Figure~\ref{fig:SineWaveDiffusionJ} shows the error versus $N$.
SSP2332 and PD-ARS schemes display third-order accuracy for the number density, $\cJ$, and second-order accuracy for $\cH_{x}$, and their errors are difficult to distinguish.
PD-ARS with SSPRK2 behaves as good as SSP2332 in the diffusion region but requires 1/3 less implicit solvers.
\begin{figure}[h]
  \centering
  \centerline{\includegraphics[width=1.2\textwidth]{figures/SineWaveDiffusion}}
%  \begin{tabular}{cc}
%    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionJ}
%    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionH}
%  \end{tabular}
   \caption{Absolute error for the number density $\cJ$ (left) and the number flux $\cH_{x}$ (right) versus number of elements for the sine wave diffusion test.  Results with different values of the scattering opacity $\sigma_{\Scatt}$, employing different IMEX schemes, are compared.  Errors with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively.  The IMEX schemes employed are:  SSP2332 ($+$), PD-ARS with SSPRK2 (circles), and PD-ARS with SSPRK3 (hexagram). Black dashed lines on the left plot reference lines proportional to $N^{-2}$ (top) and $N^{-3}$ (bottom), respectively. Black dashed line on the right plot reference lines proportional to $N^{-2}$ .}
   \label{fig:SineWaveDiffusionJ}
\end{figure}

\subsection{Neutrino Stationary State Test} \label{se: Neutrino Stationary State Test}
Next we consider a more ``realistic'' test: two-dimensional neutrino transport with emission, absorption, and elastic scattering through a stationary background.
This is designed to test the realizability-preserving properties of the PD-ARS schemes.
Figure~\ref{fig:NeutrinoStationaryTestEOS} plots the thermal state and the opacities we used.
This test is constructed on a two-dimensional domain $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,200], x^{2}\in[0,200]\}$ with a grid of 128 elements in each direction.
We take 10 energy groups from 0~MeV to 300~MeV and initialize the neutrino number density $\cJ$ and flux density $\bcH$ both at zero(arbitrarily small).
For the realizability-preserving test, we employ the CB closure with PD-ARS schemes, SSP2332, a scheme proposed by Cavaglieri \& Bewley \cite{cavaglieriBewley2015}, and a scheme proposed by McClarren et al \cite{mcclarren_etal_2008} are all applied.
Only PD-ARS schemes produce realizability-preserving results and evolve the model to a steady state.
The other schemes crashed immediately after several steps.
The realizability-preserving plot and the evolve process of PD-ARS schemes are given in Figure~\ref{fig:NeutrinoStationaryTestEvolve}.

### 2018-10-18 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Backup the modification in time integration section.

\subsection{Standard Implicit-Explicit Scheme}
Treating $\vect{\cT}$ explicitly and $\f{1}{\tau}\,\vect{\cQ}$ implicitly, a standard $s$-stage IMEX scheme takes the following form \cite{pareschiRusso_2005}
\begin{align}
  \vect{u}^{(i)}
  &=\vect{u}^{n}
  +\dt\sum_{j=1}^{i-1}\tilde{a}_{ij}\,\vect{\cT}(\vect{u}^{(j)})
  +\dt\sum_{j=1}^{i}a_{ij}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(j)}),
  \quad i=1,\ldots,s, \label{imexStages} \\
  \vect{u}^{n+1}
  &=\vect{u}^{n}
  +\dt\sum_{i=1}^{s}\tilde{w}_{i}\,\vect{\cT}(\vect{u}^{(i)})
  +\dt\sum_{i=1}^{s}w_{i}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(i)}), \label{imexIntermediate} 
\end{align}
where  $(\tilde{a}_{ij})$ and $(a_{ij})$ are coefficients of the $i$-th stage and they are the elements of matrices $\tilde{A}$ and $A$, respectively.
The vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weight vectors.
These coefficients and weights have to satisfy certain condition for an accurate, convergent and stable scheme.
For instance, to have second-order temporal accuracy, the following conditions are required:
\begin{equation}
  \sum_{i=1}^{s}\tilde{w}_{i}=\sum_{i=1}^{s}w_{i}=1,
  \label{orderConditions1}
\end{equation}
and
\begin{equation}
  \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}
  =\sum_{i=1}^{s}\tilde{w}_{i}\,c_{i}
  =\sum_{i=1}^{s}w_{i}\,\tilde{c}_{i}
  =\sum_{i=1}^{s}w_{i}\,c_{i}=\f{1}{2}, 
  \label{orderConditions2}
\end{equation}
where $\tilde{c}_{i} = \sum_{j}^{s}\tilde{a}_{ij}$ and $c_{i}=\sum_{j}^{s}a_{ij}$.

@@

It can be proven that the conditions we need for a simple convex-invariant IMEX scheme are: \cite{chu_etal_2018}
\begin{enumerate}
    \item Consistency of the implicit coefficients:
    \begin{equation}
      \sum_{i=1}^{s}w_{i}=1.
    \end{equation}
    \item Second-order accuracy in the streaming limit:
    \begin{equation}
      \sum_{i=1}^{s}\tilde{w}_{i}=1
      \quad\text{and}\quad
      \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}=\f{1}{2},
      \label{eq:orderConditionsEx}
    \end{equation}
    \item Convex-invariant:
    \begin{align}
      &a_{i1} = 0, \quad \text{for} \quad i=1,\ldots,s, \nonumber \\
      &a_{ii}>0, \quad c_{i0},\tilde{c}_{i0}\ge0, \quad \text{for} \quad i=2,\ldots,s, \nonumber \\
      &\text{and} \quad c_{ij},\tilde{c}_{ij}\ge0, \quad \text{for} \quad i=3,\ldots,s, \quad\text{and}\quad j=2,\ldots,i-1.  
    \end{align}
    with $\sum_{j=0}^{i-1}c_{ij}=1$, for $i=1,\ldots,s$, and $c_{\Sch}=\min_{\substack{i = 2,\ldots,s \\ 
                  j = 0,2,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}}>0$.
    And $c_{ij}$ and $\hat{c}_{ij}$ be given by
    \begin{equation}
     \begin{aligned}
      c_{i0} &= 1-\sum_{j=2}^{i-1}\sum_{l=j}^{i-1}a_{il}b_{lj}, \quad &
      c_{ij} &= \sum_{l=j}^{i-1}a_{il}b_{lj} \\
      \tilde{c}_{i0} &= \tilde{a}_{i1}+\sum_{j=2}^{i-1}a_{ij}\tilde{b}_{j1}, \quad &
      \tilde{c}_{ij} &= \tilde{a}_{ij}+\sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj}.  
     \end{aligned}
     \label{eq:positivityCoefficientsARS}
    \end{equation}
    \begin{equation}
      b_{ii} = \f{1}{a_{ii}}, \quad
      b_{ij} = -\f{1}{a_{ii}}\sum_{l=j}^{i-1}a_{il}b_{lj}, \quad
      \tilde{b}_{ij} = -\f{1}{a_{ii}}\Big(\tilde{a}_{ij}+\sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj}\Big).  
    \end{equation}
    Note that $c_{i1}=\tilde{c}_{i1}=0$ in Eq.~\eqref{eq:positivityCoefficientsARS} so that $\sum_{j=0}^{i-1}c_{ij}=1$.
    \item Well-behaved in the diffusion limit:
    \begin{equation}
      \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s,
      \label{eq:diffusionCondition}
    \end{equation}
    where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix.
    \item Less than four stages ($s\le3$).
    \item Globally stiffly accurate: $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$. (GSA)
\end{enumerate}  
We call the IMEX scheme satisfying the above conditions {PD-ARS}. (Definition 3 in \cite{chu_etal_2018}.)
We give two optimized PD-ARS schemes here: PD-ARS with SSPRK2 and  PD-ARS with SSPRK3. 
They have second- and third-order accuracy in the streaming limit, respectively.
\subsubsection{PD-ARS with SSPRK2}
Here we give a family of PD-ARS with SSPRK2 in the standard double Butcher tableau form: explicit tableau on the left ($\tilde{A}$), implicit tableau on the right ($A$):
\begin{equation}
  \begin{array}{c | c c c}
  	0 & 0   & 0 & 0 \\
  	1 & 1   & 0 & 0 \\
  	1 & 1/2 & 1/2 & 0 \\ \hline
  	  & 1/2 & 1/2 & 0
  \end{array}
  \qquad
  \begin{array}{c | c c c}
  	0 & 0 & 0            & 0            \\
  	1 & 0 & 1            & 0            \\
  	1 & 0 & 1/2-\epsilon & 1/2+\epsilon \\ \hline
  	  & 0 & 1/2-\epsilon & 1/2+\epsilon
  \end{array}
\end{equation}
and $\epsilon \in [0, 1/2)$.
For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 2\epsilon$.
The optimized scheme ($c_{\mbox{\tiny Sch}}= 1$) is given by $\epsilon = 0$.
We chose $\epsilon = 0.1$ for the numerical test in Section~\ref{se:NumericalTests}.

\subsubsection{PD-ARS with SSPRK3}
Here we give the optimized PD-ARS with SSPRK3.
Its standard double Butcher tableau are (explicit tableau on the left, implicit tableau on the right)
\begin{equation}
  \begin{array}{c | c c c c}
  	    &     &     &     &  \\
  	 1  & 1   &     &     &  \\
  	1/2 & 1/4 & 1/4 &  \\
  	 1  & 1/6 & 1/6 & 2/3 &  \\ \hline
  	    & 1/6 & 1/6 & 2/3 &
  \end{array}
  \qquad
  \begin{array}{c | c c c c}
  	0 & 0 & 0            & 0            \\
  	1 & 0 & 1            & 0            \\
  	1/2 & 0 & 1/4 & 1/4 \\ 
  	1 & 0 & 1/6 & 1/6 & 2/3\\\hline
  	  & 0 & 1/6 & 1/6 & 2/3
  \end{array}
\end{equation}
For this schemes, $c_{\mbox{\tiny Sch}}= 1$.

>>>>

\subsection{Standard Implicit-Explicit Scheme}
Treating $\vect{\cT}$ explicitly and $\f{1}{\tau}\,\vect{\cQ}$ implicitly, a standard $s$-stage IMEX scheme takes the following form \cite{pareschiRusso_2005}
\begin{align}
  \vect{u}^{(i)}
  &=\vect{u}^{n}
  +\dt\sum_{j=1}^{i-1}\tilde{a}_{ij}\,\vect{\cT}(\vect{u}^{(j)})
  +\dt\sum_{j=1}^{i}a_{ij}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(j)}),
  \quad i=1,\ldots,s, \label{imexStages} \\
  \vect{u}^{n+1}
  &=\vect{u}^{n}
  +\dt\sum_{i=1}^{s}\tilde{w}_{i}\,\vect{\cT}(\vect{u}^{(i)})
  +\dt\sum_{i=1}^{s}w_{i}\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(i)}), \label{imexIntermediate} 
\end{align}
where  $(\tilde{a}_{ij})$ and $(a_{ij})$ are coefficients of the $i$-th stage and they are the elements of matrices $\tilde{A}$ and $A$, respectively.
The vectors $\tilde{\vect{w}}=(\tilde{w}_{1},\ldots,\tilde{w}_{s})^{T}$ and $\vect{w}=(w_{1},\ldots,w_{s})^{T}$ are the weight vectors.
These coefficients and weights have to satisfy certain condition for an accurate and consistent scheme.
For instance, to have second-order temporal accuracy, the following conditions are required:
\begin{equation}
  \sum_{i=1}^{s}\tilde{w}_{i}=\sum_{i=1}^{s}w_{i}=1,
  \label{orderConditions1}
\end{equation}
and
\begin{equation}
  \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}
  =\sum_{i=1}^{s}\tilde{w}_{i}\,c_{i}
  =\sum_{i=1}^{s}w_{i}\,\tilde{c}_{i}
  =\sum_{i=1}^{s}w_{i}\,c_{i}=\f{1}{2}, 
  \label{orderConditions2}
\end{equation}
where $\tilde{c}_{i} = \sum_{j}^{s}\tilde{a}_{ij}$ and $c_{i}=\sum_{j}^{s}a_{ij}$.

@@

It can be proven that the conditions we need for a simple convex-invariant IMEX scheme are: \cite{chu_etal_2018}
\begin{enumerate}
    \item Consistency of the implicit coefficients:
    \begin{equation}
      \sum_{i=1}^{s}w_{i}=1.
    \end{equation}
    \item Second-order accuracy in the streaming limit:
    \begin{equation}
      \sum_{i=1}^{s}\tilde{w}_{i}=1
      \quad\text{and}\quad
      \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}=\f{1}{2},
      \label{eq:orderConditionsEx}
    \end{equation}
    \item Convex-invariant:
    \begin{align}
      &a_{i1} = 0, \quad \text{for} \quad i=1,\ldots,s, \nonumber \\
      &a_{ii}>0, \quad c_{i0},\tilde{c}_{i0}\ge0, \quad \text{for} \quad i=2,\ldots,s, \nonumber \\
      &\text{and} \quad c_{ij},\tilde{c}_{ij}\ge0, \quad \text{for} \quad i=3,\ldots,s, \quad\text{and}\quad j=2,\ldots,i-1.  
    \end{align}
    with $\sum_{j=0}^{i-1}c_{ij}=1$, for $i=1,\ldots,s$, and $c_{\Sch}=\min_{\substack{i = 2,\ldots,s \\ 
                  j = 0,2,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}}>0$.
    And $c_{ij}$ and $\hat{c}_{ij}$ be given by
    \begin{equation}
     \begin{aligned}
      c_{i0} &= 1-\sum_{j=2}^{i-1}\sum_{l=j}^{i-1}a_{il}b_{lj}, \quad &
      c_{ij} &= \sum_{l=j}^{i-1}a_{il}b_{lj} \\
      \tilde{c}_{i0} &= \tilde{a}_{i1}+\sum_{j=2}^{i-1}a_{ij}\tilde{b}_{j1}, \quad &
      \tilde{c}_{ij} &= \tilde{a}_{ij}+\sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj}.  
     \end{aligned}
     \label{eq:positivityCoefficientsARS}
    \end{equation}
    \begin{equation}
      b_{ii} = \f{1}{a_{ii}}, \quad
      b_{ij} = -\f{1}{a_{ii}}\sum_{l=j}^{i-1}a_{il}b_{lj}, \quad
      \tilde{b}_{ij} = -\f{1}{a_{ii}}\Big(\tilde{a}_{ij}+\sum_{l=j+1}^{i-1}a_{il}\tilde{b}_{lj}\Big).  
    \end{equation}
    Note that $c_{i1}=\tilde{c}_{i1}=0$ in Eq.~\eqref{eq:positivityCoefficientsARS} so that $\sum_{j=0}^{i-1}c_{ij}=1$.
    \item Well-behaved in the diffusion limit:
    \begin{equation}
      \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s,
      \label{eq:diffusionCondition}
    \end{equation}
    where $\vect{e}_{i}$ is the $i$th column of the $s\times s$ identity matrix.
    \item Less than five stages ($s\le4$).
    \item Globally stiffly accurate: $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$. (GSA)
\end{enumerate}  
We call the IMEX scheme satisfying the above conditions {PD-ARS}. (Definition 3 in \cite{chu_etal_2018}.)
We give two optimized PD-ARS schemes here: PD-ARS with SSPRK2 and  PD-ARS with SSPRK3. 
They have second- and third-order accuracy in the streaming limit, respectively.
\subsubsection{PD-ARS with SSPRK2}
Here we give the optimized PD-ARS with SSPRK2 in the standard double Butcher tableau form: explicit tableau on the left ($\tilde{A}$), implicit tableau on the right ($A$):
\begin{equation}
  \begin{array}{c | c c c}
  	0 & 0   & 0 & 0 \\
  	1 & 1   & 0 & 0 \\
  	1 & 1/2 & 1/2 & 0 \\ \hline
  	  & 1/2 & 1/2 & 0
  \end{array}
  \qquad
  \begin{array}{c | c c c}
  	0 & 0 & 0            & 0            \\
  	1 & 0 & 1            & 0            \\
  	1 & 0 & 1/2 & 1/2 \\ \hline
  	  & 0 & 1/2 & 1/2
  \end{array}
\end{equation}
For this scheme, $c_{\mbox{\tiny Sch}}= 1$ and only two implicit solver are needed for each time step.
\subsubsection{PD-ARS with SSPRK3}
Here we give the optimized PD-ARS with SSPRK3.
Its standard double Butcher tableau are (explicit tableau on the left, implicit tableau on the right)
\begin{equation}
  \begin{array}{c | c c c c}
  	    &     &     &     &  \\
  	 1  & 1   &     &     &  \\
  	1/2 & 1/4 & 1/4 &  \\
  	 1  & 1/6 & 1/6 & 2/3 &  \\ \hline
  	    & 1/6 & 1/6 & 2/3 &
  \end{array}
  \qquad
  \begin{array}{c | c c c c}
  	0 & 0 & 0            & 0            \\
  	1 & 0 & 1            & 0            \\
  	1/2 & 0 & 1/4 & 1/4 \\ 
  	1 & 0 & 1/6 & 1/6 & 2/3\\\hline
  	  & 0 & 1/6 & 1/6 & 2/3
  \end{array}
\end{equation}
For this schemes, $c_{\mbox{\tiny Sch}}= 1$.
Three implicit solver are taken for each time step.
Since PD-ARS with SSPRK3 is as accurate as PD-ARS with SSPRK2 in collision involved region, see Section~\ref{se:NumericalTests} for the plots, it may not offer any advantage.
